Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-08-01 Moltres.tex
unneccessary that is
rephrase

Building on the massively parallelizable \gls{MOOSE} framework allows Moltres
to be run on super-computing platforms like \gls{NCSA}'s Blue Waters. For some
three-dimensional simulations, the number of
elements in the mesh and total number of degrees of freedom exceed one million
and ten million respectively. To handle problems of this size, Moltres has been
run on up to 608 cores. However, reducing the problem dimension from three to
two and using a structured mesh that can be much more coarse in the axial
direction allows the problem to be solved on a single core in under
five minutes.

@@

\Cref{fig:moltres_radial_fluxes} compares the fast and thermal neutron fluxes at the
reactor mid-plane ($z=H/2$). Local thermal flux growth and fast flux decay in
moderator regions and visa versa in fuel regions are apparent. The flux
magnitudes are in good agreement with the magnitudes from the \gls{MSRE} design
calculations \cite[p. 92]{briggs_molten-salt_1964} as shown in
\cref{fig:msre_radial_fluxes}. The peak fast to thermal flux ratio is
approximately 3.5 in the \gls{MSRE} design calculation as opposed to a ratio of
3 for the Moltres calculation. The depression in the thermal flux in
\cref{fig:msre_radial_fluxes} is caused by control rod thimbles and an extra
volume of surrounding fuel that is not included in the Moltres calculations.

>>>>

Building on the massively parallelizable \gls{MOOSE} framework allows Moltres
to run on super-computing platforms like the Blue Waters supercomputer at the \gls{NCSA}. For some
three-dimensional simulations, the number of
elements in the mesh and total number of degrees of freedom exceed one million
and ten million respectively. To handle problems of this size, Moltres has been
run on up to 608 cores. However, reducing the problem dimension from three to
two and using a structured mesh that can be much more coarse in the axial
direction allows the problem to be solved on a single core in under
five minutes.

@@

\Cref{fig:moltres_radial_fluxes} compares the fast and thermal neutron fluxes at the
reactor mid-plane ($z=H/2$). Local thermal flux growth and fast flux decay in
moderator regions and visa versa in fuel regions are apparent. The flux
magnitudes are in good agreement with the magnitudes from the \gls{MSRE} design
calculations \cite[p. 92]{briggs_molten-salt_1964} as shown in
\cref{fig:msre_radial_fluxes}. The peak fast to thermal flux ratio is
approximately 3.5 in the \gls{MSRE} design calculation as opposed to a ratio of
3 for the Moltres calculation. The depression in the thermal flux in
\cref{fig:msre_radial_fluxes} is caused by control rod thimbles and an extra
volume of surrounding fuel not included in the Moltres calculations.
